Modern Graph Generators: A Survey

### 2018-10-19 generators_LinkedData.tex
Graphalytics and Graph 500 corrections

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark considers a media or a publishing organization that deals with large volumes of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).

>>>>

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark considers a media or a publishing organization that deals with large volumes of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).

### 2018-10-19 generators_analytics.tex
Graphalytics and Graph 500 corrections

\paragraph{Graphalytics} Graphalytics\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}. It involves 6 real-world datasets and 2 synthetic datasets generated so that they cover two commonly used types of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}). The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths. The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} that measures the required time to preprocess and convert the graph into a suitable format for a graph processing system, or \emph{Makespan} that measures the total  execution time of a benchmarking workload algorithm. The benchmark also describes experiments for measuring the scalability of the systems under test. To facilitate the end user job of running the designed experimental workload, the benchmark provides  a performance evaluation framework, Granula\footnote{\url{https://github.com/atlarge-research/granula}}.%, that consists of three main components: modeler, archiver, and the visualizer.

>>>>

%\paragraph{Graphalytics} Graphalytics\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}. It involves 6 real-world datasets and 2 synthetic datasets generated so that they cover two commonly used types of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by the Graph 500 benchmark~\cite{Graph500}.\footnote{Hence, we do not involve it in Table~\ref{tab:comparisonCharacteristics}, because it does not bring any new generator.} The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths. The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} that measures the required time to preprocess and convert the graph into a suitable format for a graph processing system, or \emph{Makespan} that measures the total  execution time of a benchmarking workload algorithm. The benchmark also describes experiments for measuring the scalability of the systems under test. To facilitate the end user job of running the designed experimental workload, the benchmark provides  a performance evaluation framework, Granula\footnote{\url{https://github.com/atlarge-research/granula}}.%, that consists of three main components: modeler, archiver, and the visualizer.

### 2018-10-19 generators_general.tex
Graphalytics and Graph 500 corrections

\paragraph {R-MAT} (\emph{R}ecursive \emph{Mat}rix) R-MAT is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-MAT can generate weighted, directed and bipartite graphs.

@@

\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
a scalable data generator which produces weighted, undirected graph as a list of
edge tuples containing the label of start vertex and end vertex together with a
weight that represents data assigned to the edge. The space of vertex  labels is
the set of integers beginning with 0. The input values required to describe the
graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
(i.e., half the average degree of a vertex in the graph). The graph generator is
a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
so in the final step the vertex labels and order of edges are randomly shuffled.
The covered operations currently involve BFS; however, the authors intend to
involve also two more types -- optimization (single source shortest path) and
edge-oriented (maximal independent set) -- and five graph-related business areas:
cybersecurity, medical informatics, data enrichment, social networks, and
symbolic networks.

>>>>

\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-MAT can generate weighted, directed and bipartite graphs.

@@

%\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
%a scalable data generator which produces weighted, undirected graph as a list of
%edge tuples containing the label of start vertex and end vertex together with a
%weight that represents data assigned to the edge. The space of vertex  labels is
%the set of integers beginning with 0. The input values required to describe the
%graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
%(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
%(i.e., half the average degree of a vertex in the graph). The graph generator is
%a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
%so in the final step the vertex labels and order of edges are randomly shuffled.
%The covered operations currently involve BFS; however, the authors intend to
%involve also two more types -- optimization (single source shortest path) and
%edge-oriented (maximal independent set) -- and five graph-related business areas:
%cybersecurity, medical informatics, data enrichment, social networks, and
%symbolic networks.
